Model Estimation

### 2020-05-13 05_estimation.Rmd
Rely on updated (custom) tidiers for sdpdep functions

```{r tidy.sarlm}
tidy.sarlm <- function(x){
  s <- summary(x)
  df <- length(s$residuals) - length(s$coefficients) - 1
  tibble(
    term = gsub("[\\(\\)]", "\\.", rownames(s$Coef)),
    estimate = s$Coef[,1],
    std.error = s$Coef[,2],
    statistic = estimate / std.error,
    p.value = 2*(pt(abs(statistic), Inf, lower.tail = FALSE))
  )
}
lapply(ols_vs_sem, tidy) %>%
  bind_rows(.id = "model") %>%
  dwplot() + scale_x_continuous(limits = c(-0.3, 1))
```

>>>>

```{r tidy.sarlm}
lapply(ols_vs_sem, tidy) %>%
  bind_rows(.id = "model") %>%
  dwplot() + scale_x_continuous(limits = c(-0.3, 1))
```
